Discovering Focused Microgenre Communities: Toy example

### 2024-01-06 qmd/02_toy-ex.qmd
updated toy ex

    kbl(a, format = "html", padding = 2, align = "c") %>% 
        column_spec(1, bold = TRUE) %>% 
        save_kable(here("Toy", "toy-sim.png"))
    #webshot(here("Toy", "toy-sim.html"), here("Toy", "toy-sim.png"))

    kbl(b, format = "html", padding = 2, align = "c") %>% 
        column_spec(1, bold = TRUE) %>% 
        save_kable(here("Toy", "toy-dis.png"))
    #webshot(here("Toy", "toy-dis.html"), here("Toy", "toy-dis.png"))
```

```{r Plotting toy example dendrogram}
    hc.res$labels <- e.names
    p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", show_labels = TRUE, cex = 1.5, lwd = 2) 
    p <- p + geom_hline(yintercept = 0.75, 
                        linetype = "dashed", 
                        color = "red", 
                        size = 1.2)
    p <- p + labs(y = "", title = "") 
    p <- p + theme(axis.line.y = element_blank(), axis.text.y = element_blank())
    p
    save_plot(here("Toy", "link-clust-toy.png"), 
              width = 40, height = 25)
```

>>>>

    kbl(a, format = "html", padding = 2, align = "c") %>% 
        column_spec(1, bold = TRUE) %>% 
        save_kable(here("Toy", "toy-sim.html"))
    webshot(here("Toy", "toy-sim.html"), here("Toy", "toy-sim.png"))

    kbl(b, format = "html", padding = 2, align = "c") %>% 
        column_spec(1, bold = TRUE) %>% 
        save_kable(here("Toy", "toy-dis.html"))
    webshot(here("Toy", "toy-dis.html"), here("Toy", "toy-dis.png"))
```

```{r Plotting toy example dendrogram}
    hc.res$labels <- e.names
    p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", 
                   show_labels = TRUE, cex = 1.5, lwd = 2) 
    p <- p + geom_hline(yintercept = 0.75, 
                        linetype = "dashed", 
                        color = "red", 
                        linewidth = 1.2)
    p <- p + labs(y = "", title = "") 
    p <- p + theme(axis.line.y = element_blank(), axis.text.y = element_blank())
    p
    save_plot(here("Toy", "link-clust-toy.png"), 
              width = 40, height = 25)
```
